---
title: "simChef: an R package"
subtitle: "useR! Conference 2022 -- Poster Session"
author:
  name: "James Duncan<sup>1</sup>, Tiffany Tang<sup>1</sup>, Corrine F. Elliott<sup>1</sup>, Philippe Boileau<sup>1</sup>, Bin Yu<sup>1</sup>"
  affiliation: "<sup>1</sup>University of California, Berkeley"
  email: jpduncan@berkeley.edu
# author:
#  name: "Tiffany Tang"
#  affiliation: "University of California, Berkeley"
date: "June 22, 2022"
logo:
  left:
    src: imgs/cal-seal.svg
    alt: "University of California, Berkeley"
  # right:
  #   src: imgs/simChef.png
  #   alt: "simChef"
  #   url: https://yu-group.github.io/simChef
output:
  html_document:
    template: template/template.html
    css: poster.css
    md_extensions: -autolink_bare_uris # disable autolinking URLs
    highlight: rstudio
---

# Overview

```{r}
plot(cars, pch = 18)
```

`simChef` is a powerful framework for designing, documenting, and deploying simulation experiments in R.

Main goals:

- Provide an intuitive grammar of simulation experiments.
- Reduce the startup time and boilerplate code needed to create simulations.
- Provide a standard and interactive way to document and visualize simulation results.
- Support small simulations on a laptop or large ones on a cluster.

# Simulation abstractions

- **Experiment**: a collection of related simulation scenarios.
- **DGP**: Data-generating process, which define the "ground truth" to generate simulation data flexibly.
- **Method**: The main objects of study in the simulation, along with baselines.
- **Evaluator**: Produce meaningful summaries and statistics of the results.
- **Visualizer**: Outputs plots, tables, R Markdown, latex, etc. to populate interactive experiment documentation.

# Grammar of simulations

```{r, eval=FALSE}
experiment <- create_experiment() %>%
  add_dgp(dgp1) %>%
  add_dgp(dgp2) %>%
  add_method(method1) %>%
  add_vary_across(
    dgp = dgp1,
    n = c(100, 1000, 10000)
  ) %>%
  add_vary_across(
    method = method1,
    lambda = c(0.1, 0.5, 1.0)
  )
results <- experiment %>%
  run_experiment()
```
